\sysfull

### 2017-08-01 paper/background.tex

Figure~\ref{fig:code_demo_incosistency} illustrates how state can become
inconsistent in an intermittent execution using cyclic redundancy check (CRC)
code from MIBench~\cite{hicks_mibench2_2016}. The code computes CRC for an
$\texttt{nBytes}$ byte message $\texttt{msg}$ with remainder $\texttt{Rmnd}$.
Even with the checkpoint at line 3 in Fig.~\ref{fig:crc_example}, the code may
compute  $\texttt{data}$ incorrectly because  of a WAR dependence between the
read of $\texttt{Rmnd}$ on line 4 and the write of $\texttt{Rmnd}$ on line 5.  
Figure~\ref{fig:crc_example_war} shows an execution of the code in which
power fails during the second loop iteration

 $\texttt{Rmnd}$ is read (line 6 in Fig.~\ref{fig:crc_example_war}), or more
specifically---updated before a new execution loop.

>>>>

Figure~\ref{fig:code_demo_incosistency} illustrates how state can become
inconsistent in an intermittent execution using cyclic redundancy check (CRC)
code from MIBench~\cite{hicks_mibench2_2016}. The code computes CRC for an
$\texttt{nBytes}$ byte message $\texttt{msg}$ with remainder $\texttt{Rmnd}$.
Even with the checkpoint at line 3 in Fig.~\ref{fig:crc_example}, the code may
compute  $\texttt{data}$ incorrectly because  of a WAR dependence between the
read of $\texttt{Rmnd}$ on line 4 and the write of $\texttt{Rmnd}$ on line 5.
Figure~\ref{fig:crc_example_war} shows an execution of the code in which power
fails during the second loop iteration.  The problem arises because line 6 of
the execution writes $\texttt{Rmnd}$ in the second iteration, but power fails
before capturing the next checkpoint.  After restarting from the checkpoint,
the update to $\texttt{data}$ at line 10 reads the value of $\texttt{Rmnd}$
that was updated before the power failure, producing an incorrect result.

### 2017-08-01 paper/texFigCode/crc_example_war.tex

$\textcolor{red}{\circlearrowright}\text{\textcolor{red}{checkpoint()}}$; //Restart iter. 2 from checkpoint; $\text{\textcolor{red}{Rmnd is stale.}}$
data = functReflectData(msg[byte]) ^ (Rmnd >> (Wdth - 8)); 
$\textcolor{red}{\times}\text{\textcolor{red}{ERROR: data updated with stale value of Rmnd}}$

>>>>

$\textcolor{red}{\circlearrowright}\text{\textcolor{red}{checkpoint()}}$; //Restart from checkpoint; $\text{\textcolor{red}{Rmnd remains updated.}}$
data = functReflectData(msg[byte]) ^ (Rmnd >> (Wdth - 8)); 
$\textcolor{red}{\times}\text{\textcolor{red}{ERROR: data updated using incorrect Rmnd value}}$
